---
title: "Time Series Notes"
author: "MB"
date: "April 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
library(fpp2)
library(tidyverse)
library(xts)
```


# exploratory analysis

## general

```{r}
# if ts object has multiple variables, will plot them with facets
autoplot(uschange, facets=TRUE)
```

## plots for spotting seasonality

```{r}
autoplot(writing)
ggseasonplot(writing)
ggsubseriesplot(hsales)
```

## plots for spotting autocorrelation
Which may be indicative of a trend, cycle or seasonality.

Lag plots are scatterplot, indicating the relationship between results at different lags. The default in `gglagplot` is to use different colors for the different seasons. I'd look at the colored version first, then uncolored. I also don't like the lines.

```{r}
autoplot(hsales)
ggAcf(hsales)
gglagplot(hsales, do.lines=FALSE)
gglagplot(hsales, do.lines=FALSE, colour=FALSE)
```

# transformations and adjustments

Get performance per day instead of month totals to equalize the months.

```{r}
# gives nr of days per period (month or quarter)
monthdays(milk)

# picks best box-cox lambda value
BoxCox.lambda(milk)
```

# residual diagnostics

```{r}
# plots diagnostics and does Ljung-Box test
checkresiduals(naive(goog200))
```

# 
























